H3: Cultural Differences in Symbolization

### 2023-07-28 H3_semi_clean.Rmd
ran extra semi-clean analyses

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

@@

fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    # + Long.Term.Orientation
                    # + Indulgence
                    # + CTL_DG
                    # + CTL_DS
                    # + CTL_C
                , data = x
            )
fit
fit_results <- summary(fit)
fit_results

>>>>

#source("set_up_data_calculate_means.R")
load("data/data_with_means_semi_clean.RData")

@@

fit <- lm(moral_identity_symbolic ~
                    # sex3
                    # + age
                     Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_DG
                    + CTL_DS
                    + CTL_C
                , data = x
            )
fit
fit_results <- summary(fit)
fit_results
